Estimating duration in the presence of misclassification

### 2024-03-29 cis-imperfect-testing.tex

In this section, I introduce a simple model of false negatives (\ie allowing $\psens < 1$) into the likelihood derived in \cref{E-perf-test:sec:model}.
The simple model, including a constant test sensitivity, means the likelihood remains tractable.

@@

Similarly, let $p_k'$, $p_{ik}'$, $p_u$, and $p_{iu}$ have the same definition as $p_k$, $p_{ik}$, $p_u$, and $p_{iu}$ respectively except replacing $O$ with $O'$ and $\vec{\nu}_k$ with $\vec{\nu}_k'$, and conditioning on $\psens$.
As before, $p'_k = 1/\Ncis p'_{i_kk}$ and $p'_u = 1/\Ncis \sum_{i=1}^{\Ncis} p'{iu}$.

@@

As I assume that there are no false positives, the infection episode must span at least the period $[r^{(b)}_k, l^{(e)}_k]$, a period starting and ending with a positive test.
This includes all $t \in \sched'_{i(j)}$ except $t = r_k^{(e)}+1$.
Therefore, the test results $\vec{y}_k$, except the test at $r_k^{(e)}+1$, are either true positives or false negatives.
This gives $t_+ = \sum_{l=1}^{m_k} y_{k,l}(t)$ true positives and $f_- = m_k - t_{k,+}$ false negatives.

>>>>

In this section, I introduce a simple model of false negatives (\ie allowing $\psens < 1$) into the likelihood derived in \cref{E-perf-test:sec:model}.
Using a simple model, in particular a constant test sensitivity, means the likelihood remains tractable.

@@

Similarly, let $p_k'$, $p_{ik}'$, $p_u$, and $p_{iu}$ have the same definition as $p_k$, $p_{ik}$, $p_u$, and $p_{iu}$ respectively except replacing $O$ with $O'$ and $\vec{\nu}_k$ with $\vec{\nu}_k'$, and conditioning on $\psens$.
As before, $p'_k = 1/\Ncis p'_{ik}$ and $p'_u = 1/\Ncis \sum_{i=1}^{\Ncis} p'_{iu}$.

@@

As I assume that there are no false positives, the infection episode must span at least the period $[r^{(b)}_k, l^{(e)}_k]$, a period starting and ending with a positive test.
This includes all $t \in \sched'_{i(j)}$ except $t = r_k^{(e)}+1$.
Therefore, the test results $\vec{y}_k$, except the test at $r_k^{(e)}+1$, are either true positives or false negatives.
This gives $t_+ = \sum_{l=1}^{m_k-1} y_{k,l}(t)$ true positives and $f_- = m_k - 1 - t_{k,+}$ false negatives.
